---
title: "Directed Acyclic Graphs"
---

## DAG of the parking spots example

```{r include=FALSE}
# Load packages
library(tidyverse)
library(dagitty)
library(ggdag)
library(ggplot2)
```

```{r}
# parking spots 
parking_spots <- dagify(
  Y ~ X,
  coords = list(x = c(X = 1, Y = 3),
                y = c(X = 1, Y = 1)),
  labels = list(X = "having parking spots",
                Y = "sales")
)

# Plot DAG
ggdag(parking_spots) +
  theme_dag() +
  geom_dag_point(color = "lightblue") +
  geom_dag_text(color = "black") +
  geom_dag_edges(edge_color = "black") +
  geom_dag_label_repel(aes(label = label))
```

## Customer satisfaction

```{r include=FALSE}
customer_sat <- readRDS("files/customer_sat.rds")
```
    
1. Regress `satisfaction` on `follow_ups`
    
```{r}
lm_sat_fol <- lm(satisfaction ~ follow_ups, data = customer_sat)
summary(lm_sat_fol)
```
         
2. Regress `satisfaction` on `follow_ups` and account for `subscription`
    
```{r}
lm_sat_fol_subs <- lm(satisfaction ~ follow_ups + subscription, data = customer_sat)
summary(lm_sat_fol_subs)
```

## Comparison of coefficients

The coefficient in the first case (Regress `satisfaction` on `follow_ups`) is negative, meaning an increase in follow-up calls is related to a decrease in satisfaction. However, when we account for `subscription` in the linear regression, the coefficient indicates a positive linear relationship between follow-up calls and satisfaction. This is due to the fact that the number of follow-up calls depends on the subscription, which also affects the satisfaction degree. Thus, `subscription` is a cofounder and we would result in an incorrect result if we do not account for `subscription` when performing regression. The DAG for the example looks like this

```{r echo=FALSE}
# Customer satisfaction
cus_sat <- dagify(
  X ~ Z,
  Y ~ Z,
  Y ~ X,
  coords = list(x = c(Y = 3, Z = 2, X = 1),
                y = c(Y = 0, Z = 1, X = 0)),
  labels = list(X = "follow_ups",
                Y = "satisfaction", 
                Z = "subscription")
)

# Plot DAG
ggdag(cus_sat) +
  theme_dag() +
  geom_dag_point(color = "lightblue") +
  geom_dag_text(color = "black") +
  geom_dag_edges(edge_color = "black") +
  geom_dag_label_repel(aes(label = label))
```

Looking at the DAG above, we see that there is an indirect effect induced by `subscription` on the direct causal effect of `follow_ups` on `satisfaction`. The indirect effect is a spurious correlation which is irrelevant for our research, but can falsify our results if we do not conditioned on it. By accounting for `subscription` when regressing `satisfaction` on `follow_ups`, we condition on `subscription` and keep it at a fixed value. Thus, the values of `satisfaction` are purely dependent on the values of `follow_ups`, and we are able to retrieve the causal effect from `follow_ups` to `satisfaction`. 

## Plot

```{r}
# Plot of first regression
ggplot(customer_sat, aes(x = follow_ups, y = satisfaction,)) +
  geom_point(color = "cornflowerblue") +
  stat_smooth(method = "lm", se = F, color = "coral2", formula = y ~ x)
```

```{r}
# Plot of second regression
ggplot(customer_sat, aes(x = follow_ups, y = satisfaction,
                            color = subscription, 
                            alpha = subscription)) +
  geom_point() +
  stat_smooth(method = "lm", se = F, formula = y ~ x) +
  scale_color_manual(values = c("Premium"="darkolivegreen3",
                                "Premium+"="cornflowerblue",
                                "Elite"="coral2")) +
  scale_alpha_manual(values = c(1,1, 1)) +
  theme(legend.position = "right")
```



