---
title: "Difference-in-Differences"
---

```{r include=FALSE}
hospdd <- readRDS("files/hospdd.rds")
library(dplyr)
```

## Mean satisfaction for treated and control hospitals

```{r}
# Treated hospitals before the treatment
mean(dplyr::pull(dplyr::filter(hospdd, hospital >= 1, hospital <= 18, procedure==0), satis))
# Treated hospitals after the treatment
mean(dplyr::pull(dplyr::filter(hospdd, hospital >= 1, hospital <= 18, procedure==1), satis))
# Control hospitals (without treatment)
mean(dplyr::pull(dplyr::filter(hospdd, hospital > 18, procedure==0), satis))
```

1. Mean satisfaction for treated hospitals before the treatment: 3.525383
2. Mean satisfaction for treated hospitals after the treatment: 4.363351
3. Mean satisfaction for control hospitals (without treatment): 3.387499

## Linear regression

```{r}
# Treated hospitals before introduction
df_A1_lm <- (dplyr::filter(hospdd, hospital >= 1, hospital <= 18, procedure == 0))
# Treated hospitals after introduction
df_A2_lm <- (dplyr::filter(hospdd, hospital >= 1, hospital <= 18, procedure == 1))
# Control hospitals
df_B_lm <- (dplyr::filter(hospdd, hospital > 18))
```

1. Linear regression on treated hospitals before introduction

```{r}
summary(lm(satis ~ as.factor(hospital) + as.factor(month), data = df_A1_lm))
```

2. Linear regression on treated hospitals after introduction

```{r}
summary(lm(satis ~ as.factor(hospital) + as.factor(month), data = df_A2_lm))
```

3. Linear regression on control hospitals

```{r}
summary(lm(satis ~ as.factor(hospital) + as.factor(month), data = df_B_lm))
```

`as.factor()` converts a vector object to a factor. We specify a regressor using `as.factor()` when the regressor is a categorical variable. We want R to treat the variable as a categorical one instead as a numeric one. In our case, the regressors "Hospital ID" and "Month" are categorical variables, thus we need to use `as.factor()`.
